Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-09-13 paper.tex
fixed sentence in 4.1

The bulk of the CRps are injected by relatively low Mach number shocks and
parametrized by $f_\rmn{p,inj}(p) = C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where
$\alpha_\rmn{inj}\approx 2.5$ in our simulations. The CRps approximately trace
the thermal gas with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
\citep{pinzke10,2016MNRAS.459...70V}, where the normalisation is fixed by the
injection rate of CR energy in the last 650~Myrs. Our simulations show that the
CR energy approximately amounts to 0.03 per cent of the thermal energy inside
the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{CR,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.0003$. The
spectrum of the initial CRp distribution is determined by the steady state
between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalisation by requiring $\int_0^{R_{200}}\eps_\rmn{CR,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.003$. Note
that the injected energy in the last 650 Myr is smaller by about a factor of 10
in comparison to the cumulative CR energy injected over the entire cosmological
history of the cluster. However, since the individual injection events of CR
energy are similar, the CRes injected during the merger are especially important
for the radio emission above 1 GHz since these CRs have not yet had time to
cool.  Similarly, the initial CRe distribution is given by the steady state
between cooling (Coulomb, inverse Compton, and synchrotron) and injection of
secondary CRes from $f_\rmn{p,0}$.  The diffusion constant $D_{pp} \propto
X_{\rm tu}^{2} \eps_{\rm th}^{\alpha_{\rm tu}-1} \sqrt{T} k_L$ is calculated for
each radial bin. All parameters and assumptions are similar to what is used for
our simulated cluster (see section~\ref{sec:results}). Our fiducial model
assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm CR, spat}=1.0$,
and $k_L=2 \upi/\lambda_L$ where $\lambda_L=100$ kpc. We also assume a fixed
acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.

>>>>

The bulk of the CRps are injected by relatively low Mach number shocks and
parametrized by $f_\rmn{p,inj}(p) = C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where
$\alpha_\rmn{inj}\approx 2.5$ in our simulations. The CRps approximately trace
the thermal gas with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
\citep{pinzke10,2016MNRAS.459...70V}, where the normalisation is fixed by the
injection rate of CR energy in the last 650~Myrs. Our simulations show that the
CR energy approximately amounts to 0.03 per cent of the thermal energy inside
the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{CR,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.0003$. The
spectrum of the initial CRp distribution is determined by the steady state
between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalisation by requiring $\int_0^{R_{200}}\eps_\rmn{CR,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.003$. Note
that the injected {\em CR energy} in the last 650 Myr is smaller by about a
factor of 10 in comparison to the cumulative CR energy injected over the entire
cosmological history of the cluster. However, since the injected {\em CR energy
  rate} averaged over the formation time of the cluster is similar to that
during a merger, the CRes injected during the merger are especially important
for the radio emission above 1 GHz since these CRs have not yet had time to
cool. Similarly, the initial CRe distribution is given by the steady state
between cooling (Coulomb, inverse Compton, and synchrotron) and injection of
secondary CRes from $f_\rmn{p,0}$.  The diffusion constant $D_{pp} \propto
X_{\rm tu}^{2} \eps_{\rm th}^{\alpha_{\rm tu}-1} \sqrt{T} k_L$ is calculated for
each radial bin. All parameters and assumptions are similar to what is used for
our simulated cluster (see section~\ref{sec:results}). Our fiducial model
assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm CR, spat}=1.0$,
and $k_L=2 \upi/\lambda_L$ where $\lambda_L=100$ kpc. We also assume a fixed
acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.
